Crowdy: Social Crowd Visualization

### 2011-04-27 docs/crowdy_gui.tex
Updated evaluation part in the report.
add future work in the report

\documentclass{sig-alternate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{subfigure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{img/UIdesign.jpg}
\caption{Crowdy User Interface Design}
\label{fig:UIdesign}
\end{figure*}

@@

Figure \ref{fig:UIdesign} shows an outline of the prototype. We want to provide
the user with a simple and flexible interface to maximize their options for
exploring while minimizing their memory overhead. Existing web applications
show that the most general task should be the main focus and the other
available options may be placed on the side or hidden according to their
frequency of usage. Since the primary function of our system is to visualize
the Crowds emerged over time, the crowd display window is our
first priority. In the crowd display window, we
consider the needs of personalization for our potential users(e.g. Analyst).
There is a global view panel and a personal workspace panel. The personal
workspace panel distinguishes from the global view panel in a way that it only
shows the set of crowds marked by the user when exploring in the global view
panel. We have tabs to help our users quickly and easily transit between these
two views. Inside each view, we need to decide the best format to condense
a massive amount of data. Each crowd has metadata associated with it such as
starting and ending time, crowd participants, topics, tweets,
location data, etc. To effectively organize these properties to assist quick
and convenient retrieval by the user, we consider these two formats: timeline
and list. For both view panels, these two formats are included but sized
unequally. The size is adjustable(in the option panel) according to the user's
need. Generally, ``timeline'' is more suitable for overview a large number of
crowds while ``list'' is better for investigating details in a smaller set of crowds. We
also provide several filtering options for both timeline and list format in the
option panel. Some detailed components in these three panels are listed below.

@@

\subsubsection{Map}

@@

The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
okay, bad, and very bad) questions, and YY open questions. The questions are
listed below:

\begin{itemize}
\item Whether the interface for timeline view is easy to use?
\item Whether the interface for list view is easy to use?
\item Whether the search feature for timeline view is easy to use?
\item Whether the search results in the timeline view could answer the information
need for your query.
\item Whether the search feature for list view is easy to use?
\item Whether the search results in the list view could answer the information
need for your query.
\item Whether 
\end{itemize}

\section{CONCLUSIONS}
In conclusion, we have implemented the Social Crowd Visualization system as a
web application that enable users to visualize,summarize and organize temporal
crowd formation on Twitter. We studied several types of potential users and
design the interface carefully to meet their needs. We implemented a few
different layout format and a search component to ease the crowd retrieval
effort on user. Finally, we design a sequence of possible evaluations for this
system. The interface will be continually improved as it is also an on-going
DARPA project with the InfoLab. As the next step, a few direction such as user
model construction and map view implementation will be carried out.

\section{FUTURE WORK}

>>>>

\documentclass{sig-alternate}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{url}
\usepackage{subfigure}

@@

@@

This section illustrate an outline of the prototype. We want to provide
the user with a simple and flexible interface to maximize their options for
exploring while minimizing their memory overhead. Existing web applications
show that the most general task should be the main focus and the other
available options may be placed on the side or hidden according to their
frequency of usage. Since the primary function of our system is to visualize
the Crowds emerged over time, the crowd display window is our
first priority. In the crowd display window, we
consider the needs of personalization for our potential users(e.g. Analyst).
There is a global view panel and a personal workspace panel. The personal
workspace panel distinguishes from the global view panel in a way that it only
shows the set of crowds marked by the user when exploring in the global view
panel. We have tabs to help our users quickly and easily transit between these
two views. Inside each view, we need to decide the best format to condense
a massive amount of data. Each crowd has metadata associated with it such as
starting and ending time, crowd participants, topics, tweets,
location data, etc. To effectively organize these properties to assist quick
and convenient retrieval by the user, we consider these two formats: timeline
and list. For both view panels, these two formats are included but sized
unequally. The size is adjustable(in the option panel) according to the user's
need. Generally, ``timeline'' is more suitable for overview a large number of
crowds while ``list'' is better for investigating details in a smaller set of crowds. We
also provide several filtering options for both timeline and list format in the
option panel. Some detailed components in these three panels are listed below.

@@

@@

The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
okay, bad, and very bad) questions, and YY open questions. The likert-scale questions
are listed below:

\begin{itemize}
\item Whether the interface for timeline view is easy to use?
\item Whether the interface for list view is easy to use?
\item Whether the search feature for timeline view is easy to use?
\item Whether the search feature for list view is easy to use?
\item Whether the search results in the timeline view could answer the information
need for your query.
\item Whether the search results in the list view could answer the information
need for your query.
\end{itemize}

Besides, here are the open questions:
\begin{itemize}
\item What are the features that you like most? Why?
\item What are the features that you don't like / hate most? Why?
\item What features that you would like Crowdy to implement in the future?
\item Any other comments? 
\end{itemize}

\section{CONCLUSIONS}
In conclusion, we have implemented the Social Crowd Visualization system as a
web application that enable users to visualize,summarize and organize temporal
crowd formation on Twitter. We studied several types of potential users and
design the interface carefully to meet their needs. We implemented a few
different layout format and a search component to ease the crowd retrieval
effort on user. Finally, we design a sequence of possible evaluations for this
system. The interface will be continually improved as it is also an on-going
DARPA project with the InfoLab.

\section{FUTURE WORK}
There are several natural extensions of this system that we will carry on in the near future. Fist of all, we see that building user model may be beneficial to enhance the user experience over different operation sessions. Currently, the user behaviors are recorded globally as if there is only one user using Crowdy. Once the user model component is implemented, we can seperate individual preference and possibly show the preference of users with different level granularity. In addition, we can better learn the user preference as different role and improve our data filtering mechanism accordingly.

Secondly, we will also consider implementing map view. The map view can better present the geographical aspect of the crowds. As a portion of the tweet data we have crawled contains location information, it would be interesting to show as a map how users in a crowd distribute.

In third, we see a need to contextually summarize the crowds. With informative keywords to represent each crowd, we can obtain more valuable search results. For example, the search of ``howdy'' should be some crowds with ``howdy'' as the main theme instead of a big crowd with ``howdy'' appears in 1 tweet only. Besides, users of the system will be able to distinquish and identify crowds of interest at a first glance. This can ease the browsing expereince of users.
